Estimating duration in the presence of misclassification

### 2024-08-01 conclusion.tex
Christl comment on study design

The challenges in estimating the distribution of the duration of detectability originated in the design of the studies used.
Exploring the design of future studies to better estimate the distribution of the duration of detectability would be beneficial.
A particularly promising direction would be intensive follow-up of individuals following a positive test (\eg daily testing) until they have two or more negative tests.
Intensive follow-up would increase the precision by which the end of the infection episode is known.
Furthermore, it reduces the impact of false negatives because they are likely to be followed by a true positive.
I have developed software that could be used to perform simulation studies of alternative designs.

>>>>

The challenges in estimating the distribution of the duration of detectability originated in the design of the studies used.
Exploring the design of future studies to better estimate the distribution of the duration of detectability would be beneficial.
A particularly promising direction would be intensive follow-up of individuals following a positive test (\eg daily testing) until they have two or more negative tests.
Intensive follow-up would increase the precision by which the end of the infection episode is known.
Furthermore, it reduces the impact of false negatives because they are likely to be followed by a true positive.

Individuals were not tested exactly on the schedule specified in the CIS protocol.
This was useful for the estimation of the distribution of the duration of detectability, because it meant that information was available at times other than exact multiples of seven.
Building in some variations in testing schedules into the protocol (\eg randomising gaps between tests) may also be a promising approach to improve the estimation of the distribution of the duration of detectability.
I have developed software that could be used to perform simulation studies of alternative designs.
